### 2025-04-09 multiple-regression.qmd
20250407 - correlation
20250408 - addressing nonindependence of observations

```{r}
library("petersenlab")
library("tidyverse")
library("knitr")
```

@@

## Impact of Oultiers {#sec-multipleRegressionOutliers}

>>>>

```{r}
library("petersenlab")
library("rms")
library("tidyverse")
library("knitr")
```

### Load Data {#sec-correlationLoadData}

```{r}
#| eval: false
#| include: false

load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_seasonal.RData", fsep = ""))
```

```{r}
load(file = "./data/player_stats_weekly.RData")
load(file = "./data/player_stats_seasonal.RData")
```

We created the `player_stats_weekly.RData` and `player_stats_seasonal.RData` objects in @sec-calculatePlayerAge.

@@

## Addressing Non-Independence of Observations {#sec-multipleRegressionNonIndependence}

```{r}
player_stats_seasonal_subset <- player_stats_seasonal %>% 
  filter(!is.na(player_id))

rms::robcov(rms::ols(
  fantasyPoints ~ height,
  data = player_stats_seasonal_subset,
  x = TRUE,
  y = TRUE),
  cluster = player_stats_seasonal_subset$player_id) #account for nested data within player
```

## Impact of Outliers {#sec-multipleRegressionOutliers}
